---
title: "RR-Project"
author: "Recep Arda Kaya & Gamze Kopal & Evrim Bilgen"
date: "9/4/2022"
output: html_document
---


## What Affects Starbucks Customer's Retention
### Backgroud

I understand that the Starbucks store in Malaysia questioned its customers to learn more about their buying behavior. The intent was to reveal the characteristics of a customer that will continue buying at Starbucks.

### Conclusion

Spending and price rating highly affect customer loyalty. A unit increase in spending category increases the odds of loyalty by a factor of 12.48. Ambiance rating and service rating positively contribute to the store's good brand image. On the other hand, improving product variety (product & choose rate) and wifi could more enhance the general brand image.

```{r}
library(tidyverse)
library(lattice)
library(caret)
library(corrplot)
library(psych)
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("Biobase")
library(NMF)
library(grid)
library(ggthemes)
library(gridExtra)
library(knitr)
```

## What Contributes to Positive Perception of Store's Brand Image

```{r}
data_cat <- read.csv("/Users/arda.kaya/Downloads/ReproducibleResearch/starbucks_editedversion.csv")
data <- read.csv("/Users/arda.kaya/Downloads/ReproducibleResearch/starbucks_editedversion_clean.xls")
data <- na.omit(data)
data_cat <- na.omit(data_cat)

data$loyal <-ifelse(data$loyal==0,1,0) # recoding loyal/disloyal customers
data <- data[,-nearZeroVar(data)] 

```


```{r}
o <- omega(data[,12:19], nfactors=3, plot=F)
omega.diagram(o, digits=2, main="Attributes of Brand Image")
```

## What Affects Customer's Loyalty: Logistic Regression
```{r}
glm_fit <- glm(loyal ~ ., data, family="binomial")
p <- predict(glm_fit, newdata = data, type = "response")
pred <- ifelse(p>0.5,1,0)
tab <- table(Predicted=pred, Actual=data$loyal)
confusionMatrix(tab)
c <- as.data.frame(glm_fit$coefficients)
c$name <- rownames(c)
colnames(c)[1] <- "coef"
c$odds <- exp(c$coef)
```

```{r}
options(repr.plot.width=13, repr.plot.height=13)

c %>% filter(name!="(Intercept)" & name!="predict") %>%  ggplot(aes(reorder(name,odds),odds)) + 
    geom_bar(stat = "identity") + 
    geom_label(aes(label=round(odds,2)),size=4) +
    coord_flip() +
    theme_fivethirtyeight() +
    theme(axis.text=element_text(size=12), plot.subtitle = element_text(size=12), plot.caption = element_text(size=12), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    geom_hline(yintercept = 1, color="red", linetype="dashed") +
    labs(title = 'Factors Affecting Customers Loyalty (Odds Ratio)', subtitle = "factors with odds ratio greater than 1 positively affect loyalty", caption = "*** interpretation: a 1 unit increase in spending category increases the odds of loyalty by a factor of 7.9 ***")

```

```{r}
options(repr.plot.width=14, repr.plot.height=7)

a <- ggplot(data,aes(spendPurchase,loyal, color=loyal)) + 
    geom_jitter(height = .01, alpha = .5) +
    stat_smooth(method="glm", method.args = list(family = "binomial"), se=F) +
    scale_y_continuous(limits=c(0,1)) +
    theme(axis.text=element_text(size=12), plot.subtitle = element_text(size=12), plot.caption = element_text(size=12)) +
    labs(title = 'How Spending Affects Loyalty', subtitle="x: spending, y: loyalty") +
    theme_fivethirtyeight()

b <- ggplot(data,aes(priceRate,loyal, color=loyal)) + 
    geom_jitter(height = .01, alpha = .5) +
    stat_smooth(method="glm", method.args = list(family = "binomial"), se=F) +
    scale_y_continuous(limits=c(0,1)) +
    theme(axis.text=element_text(size=12), plot.subtitle = element_text(size=12), plot.caption = element_text(size=12)) +
    labs(title = 'How Price Rating Affects Loyalty', subtitle="x: price rating, y: loyalty") +
    theme_fivethirtyeight()

grid.arrange(a,b, nrow=1)
```


## Customer's Segmentation Using Matrix Factorization
```{r}
fit <- nmf(data[,-1], 5, "lee", seed=14) 
options(repr.plot.width=5, repr.plot.height=5)
ht <- grid.grabExpr(coefmap(fit, color = "YlOrRd:50", scale = "c1", main="Decomposing Survey to 5 Groups", fontsize=4, cexCol=4/1, cexRow=4/1, tracks=NA))
grid.newpage()
pushViewport(viewport(angle = 90))
grid.arrange(ht, heights=15)
#popViewport()
```

```{r}
# clustering
w <- basis(fit)
type <- max.col(w) 
data$cluster <- type
```
## Table: Groups of Customers After Clustering
```{r}
cluster <- data %>% group_by(cluster) %>% summarise(n=n(), STATUS=median(status), AGE=mean(age), SPEND=median(spendPurchase), 
                                                    PRICE=round(mean(priceRate),1), SERVICE=round(mean(serviceRate),1), 
                                                    AMBIANCE=round(mean(ambianceRate),1), LOYAL=round(mean(loyal),1))

# recoding categorical variables for better readability
cluster[,'AGE'] <- c("20 to 29","20 to 29","20 to 29","20 to 29","20 to 29")
cluster[,'STATUS'] <- c("employed","student","employed","employed","student")
cluster[,'SPEND'] <- c("less than 20","less than 20","less than 20","20 to 40","20 to 40")

kable(cluster, caption="Groups of Customers After Clustering")
```

```{r}

```